
%%% \newcommand{\namx}[1]{#1}% to be replace with \name
\selectlanguage{czech}
\begin{enumerate}[label={[\arabic*]}]

\selectlanguage{french}
\item \name{P.L.BAETSLE}: \orig{143} Méthode des moindres carrés.  Sur
  les observations indirectes dont les paramětres sont liés par des
  éguations de conditions, et sur la construction de fonetions sans
  corrélation a posteriori. Bull. trimest. Soc. belge Photogr.,1964,
  76, 18--33.

% @article{DBLP:journals/cacm/Barrodale70,
%   author    = {Ian Barrodale},
%   title     = {Certification of algorithm 127 {[F5]:} Ortho},
%   journal   = {Commun. {ACM}},
%   volume    = {13},
%   number    = {2},
%   pages     = {122},
%   year      = {1970},
%   url       = {https://doi.org/10.1145/362007.362049},
%   doi       = {10.1145/362007.362049},
%   timestamp = {Tue, 06 Nov 2018 00:00:00 +0100},
%   biburl    = {https://dblp.org/rec/journals/cacm/Barrodale70.bib},
%   bibsource = {dblp computer science bibliography, https://dblp.org}
% }
%
\selectlanguage{english}
\item \name{I.BARRODALE}: Certification of Algorithm 127 -
  Ortho, Commun.  ACM, 13(1970), 122.

\item \name{F.L.BAUER}: Elimination with Weighted Row Combinations
  for Solving Linear Eguations and Least Sguares Problems. Num.
  Math., 7(1965), 338--352.

\selectlanguage{german}
\item \name{P.BREUER}: Orthogonslisierung - ein Verfahren zur direkten
  Auflösung von Fehlergleichungssystemen unter Umgehung des
  Normalzleichungssystems. Allg. Verm.-Nachr., 76(1969), 11, 478--480.

\selectlanguage{russian}
\item \name{Г.А.БУРМИСТРОВ}: Основы способа наименьших
квадратов. Госгеол- техиздат, Москва 1963.

\selectlanguage{english}
\item \name{B.CVETKOV}, \name{J.E.LILLY}: Triangulation Adjustment by
  Orthogonalization. Canad. Surv., XII(1955), 6, 396--414.

\item \name{B.CVETKOV}: On the "Indefinite" Solution of a Linear
  System by the Principle of Least Squares. Empire Survey Review,
  XIII(1956), 100, 272--282.

\item \name{B.CVETKOV}: The Number of Conditional Eguations Reguired
  for the Adjustment of a Trigonometrical Net. Empire Survey Review,
  XIV(1957), 103, 24--34.

\item \name{B.CVETKOV}: On the Least Sguares Ad justment of Arbitrary
  Inconsistent Linear Eguations. Survey Review, XVII(1963), 128,
  89--95.

\selectlanguage{russian}
\item \name{Н.Д.ДРОЗДОВ}: О решении линейных систем при уравнивании
  геодезических сетей. Труды МИИГАиК, 1960, вып. 39, 83--88.

\item \name{Н.Д.ДРОЗДОВ}: Решение условных уравнений методом
  ортогонализации.  Труды МИИГАиК, 1960, вып. 42, 23--33.

  % ------------------------------------------------------------------

\selectlanguage{czech}
\item \name{D.K.FADDĚJEV}, \name{V.N.FADDĚJEVOVÁ}: \orig{144}
  Numerické metody lineární algebry. SNTL, Praha 1964.

\selectlanguage{russian}
\item \name{Д.К.ФАДДЕЕВ}, \name{В.Н.КУБЛАНОВСКАЯ},
  \name{В.Н.ФАДДЕЕВА}: С решении линейных алгебраических систем с
  прямоугольными матрицами.  Труды мат. инст. АНСССР, 1968, т. 96,
  76--92.

\selectlanguage{english}
\item \name{G.E.FORSYTHE}: Generation and Use of Orthogonal
  Polynomials for Data-fitting with a Digital
  Computer. J. Soc. Indust.  Appl. Math., 5(1957), 74--87.

\selectlanguage{russian}
\item \name{Дж.ФОРСАЙТ}, \name{К.МОЛЕР}: Численное решение систем
  линейных ал- гебраических уравнений. Мир, Москва 1969.

\selectlanguage{polish} % {polish} J.Gaździcki
\item \name{J.GAŹDZICKI}: Nowe algorytmy wyrównania metodą
  najmniejszych kwadratów.  Prace Inst. geod. i kart.,tom
  XIII(1966),2, 86--126.

\selectlanguage{english}
\item \name{J.GAŹDZICKI}: On an Algorithm of Adjustment by the Method
  of Least Sguares. Bull. géod., 1967, 85, 211--221.

\selectlanguage{russian}
\item \name{И.М.ГЕРАСИМОВ}: Решение условных уравнений и уравнений
  поправок по способу последовательных преобразований. Геод. и карт.,
  1958, 7, 5--14.

\selectlanguage{english}
\item \name{F.CHARAMZA}: Automatic Programming of Least Sauares
  Adjustment Problems. Bull. géod., 1967, 86, 457-468.

\selectlanguage{czech}
\item \name{F.CHARAMZA}: Programovací systém MNČ - E503. Výzk. zpráva
  VÚGTK č. 290, Praha 1968.


\item \name{F.CHARAMZA}: Programy MNČ-ODRA, MNČ-ODRA-VM a MNČ-ODRA-ZP
  pro řešení úloh vyrovnávacího počtu na samočinném počítači
  ODRA-1003. Edice VÚGTK, řada 3, Praha 1969.

\selectlanguage{german}
\item \name{K.LINKWITZ}: Über die nachträgliche Berücksichtigung von
  Beobachtungzen bei der Ausgleichung von A vermittelnden
  Beobachtungen. Z. Verm.-Wes., 93(1968), 11, 430--439.

\selectlanguage{russian}
\item \name{З.М.ЮРШАНСКИЙ}: Многогрупповое уравнивание методом
  последовательной ортогонализации условных уравнений. Труды НИИГАиК,
  13(1960), 49--57.

\item \name{Е.Н.КАПУСТИНА}: Алгоритмы решения систем линейных
  алгебраических уравнений. Алгор. и алгор. языки, 1969, вып. 4,
  34--47.

  % ---------------------------------------------------------------

\selectlanguage{english}
\item \name{K.R.KOCH}, \name{A.J.POPE}: \orig{145} Least Squares
  Adjustment with Zero Variances. Z. Verm.-Wes., 94(1969), 10,
  390--393.

\selectlanguage{german}
\item \name{P.LAUCHLI}: Jordan-Elimination und Ausgleichung nach kleinsten
  Quadraten. Num. Math., 3(1961), 226--240,

\selectlanguage{english}
\item \name{J.E.LILLY}: Letter to the Editor. Canad. Surv., XII(1955),
  8, 550.

\selectlanguage{russian}
\item \name{А.И.МАЗМИШВИЛИ}: Способ наименыших квадратов. Недра,
  Москва 1968.

\selectlanguage{english}
\item \name{J.R.RICE}: Experiments on Gram-Schmidt Orthogonalization.
  Math. Comput., 20(1966), 325--328.

\selectlanguage{german}
\item \name{H.RUTISHAUSER}: Algorithmus 2. Orthonormierung von
  Vektoren nach \name{E.SCHMIDT}. Computing, 1(1966), 159--161.

\selectlanguage{english}
\item \name{E.SCHMID}: Letter to the Editor. Canad. Surv., XII(1955),
  7, 484--487.

\item \name{E.SCHMID}, \name{A.J.McNAIR}: Orthonormal Eguations for
  Surveying Adjustment. Discussion. J. Surv. Mapp.
  Div. Amer. Soc. Civil Engrs.,  89(1963), SU 3, 201--212.

\selectlanguage{german}
\item \name{H.H.SCHMID}: Ein allgemeiner Ausgleichungs-Algorithmus zur
  Auswertung von hybriden Messanordnungen. Bildmess. und
  Luftbildwesen, 33(1965),3, 93 - 102, 4, 173--176.

\item \name{H.R.SCHWARZ}, \name{H.RUTISHAUSER}, \name{E.STIEFEL}:
  Numerik symnetrischer Matrizen. Teubner, Stuttgart 1968.

\selectlanguage{english}
\item \name{H.L.SU}: Orthonormai Eguations for Surveying
  Adjustment. J.  Surv. Mapp. Div. Proc. Amer. Soc. Civil Engrs.,
  89(1963), SU 1, 77--90.

\item \name{H.L.SU}: Orthonormal Eguations for Surveying
  Adjustments. Closure. J. Surv. Mapp. Div. Amer. Soc. Civil Engrs.,
  90(1964), SU 2, 171--173.

\selectlanguage{russian}
\item \name{Г.Е.ШИЛОВ}: Математический анализ
(конечномерные линейные пространства). Наука, Москва 1969.

\selectlanguage{english}
\item \name{J.TODD}: Jurvey cf Numerical Analysis. McGraw-Hill,
  N. York 1962.

% -----------------------------------------------------------------

\selectlanguage{russian}
\item \name{И.ТРЕНКОВ}: \orig{146} Метод за решаване системи нормални
  уравнения при изравнение на големи
  мрежи. Изв. центр. лаб. геод. Вълг. АН, 1963, кн. 4, 69--81.

\item \name{И.ТРЕНКОВ}: Определяне на неизвестните при посредствено из-
равнение и на поправките при условно изравнение в случай на
големи триангулачни мрежи без съставяне на нормални уравнения.
Изв. центр. лаб. геод. Бълг. АН, 1965, кн. 6, 79--90.

\item \name{В.В.ВОЕВОДИН}: Численные методы алгебры (теория и
  алгорифмы).  Наука, Москва 1966.

\selectlanguage{english}
\item \name{P.J.WALSH}: Algorithm 127 - ORTHO. Commun. ACM, 5(1962),
  911--513.

\item \name{H.WOLF}: Ausgleichungsrechnung nach der Methode der
  kleinsten Guadrate. Dümmler, Bonn 1968.

\selectlanguage{czech}
\item \name{I.BABUŠKA}, \name{M.PRÁGER}, \name{E.VITÁSEK}: Numerické
  řešení diferenciálních rovnic. SNTL, Praha 1964.

\selectlanguage{english}
\item \name{P.G.BEHRENZ}: Algorithm 133 - RANDOM. Commun. ACM,
  5(1962), 553.

\item \name{P.G.BEHRENZ}: Remark on Algorithm 133 -
  RANDOM. Commun. ACM, 5(1962), 606.

\selectlanguage{russian}
\item \name{Р.ВЕЛЛМАН}: Введение в теорию матриц. Наука, Москва 1969.

\selectlanguage{english}
\item \name{A.BJERHAMMAR}: Matrix Algebra. Ref. č. 507D z
  XII. kongresu FIG, Londýn 1968, 23--26.

\selectlanguage{czech}
\item \name{J.BOHM}: Vyrovnávací počet. SNTL, Prahe 1964.

\selectlanguage{english}
\item \name{P.BUSINGER}, \name{G.H.GOLUB}: Linear Least Squares
  Solutions by Householder Transformations. Numerische Mathematik,
  7(1965), 269--276.

\item \name{G.H.GOLUB}: Numerical Methods for Solving Linear least
  Sguares Problems. Numerische Mathematik, 7(1965), 206--216.

\item \name{G.H.GOLUB}: Numerical Methods for Solving Linear Least
  Sguares Problems. Aplikace matematiky, 10(1965), 3, 213--216.

  % ----------------------------------------------------------

\item \name{G.H.GOLUB}: \orig{147} Least Sguares, Singular Values and
  Matrix Approximations. Aplikace matematiky, 13(1968), 1, 44---51.

\selectlanguage{russian}
\item \name{Л.П.ГРАВАРЬ}: Таблицы полиномов
  Чебышева, ортонормированных на системе равноотстоящих
  точек. Выч. центр АН СССР, Москва 1965.


\selectlanguage{english}
\item \name{D.L.LAUGHLIN}: Remark on Algorithm 133 - RANDOM. Commun.
  ACM, 6(1963), 105.

\item \name{E.H.MOORE}: General Analysis. Mem. Amer. Phil. Soc.,
  9(1935).

\item \name{H.H.SCHMID}, \name{E.SCHMID}: A Generalized Least Sguares
  Solution for Hybrid Measuring Systems. Canad. Surv., 19(1965), 1,
  27--41.

\item \name{L.COLLATZ}: Funkcionální analýza a numerická matematika.
  SNTL, Praha 1970.

\end{enumerate}

~

\selectlanguage{czech}
\begin{flushright}
  \begin{tabular}[t]{l}
    Recenzenti:\\[1ex]
    \hspace{5ex}prof. Ing. dr. Josef Böhm, DrSc.  \\
    \hspace{5ex}prof. Ing. dr. Josef Vykutil      \\
    \hspace{5ex}doc. RNDr. Zbyněk Nádeník, DrSc.  \\
    \hspace{5ex}Ing. Vladimír Radouch, CSc.       \\

  \end{tabular}
\end{flushright}
